Carbonate chemistry at Ny-Ålesund

### 2023-06-02 awipev-CO2.Rmd
Added air-sea CO2 flux estimates with Dobashi

count_depth <- depth_time(tmp) %>% 
  dplyr::filter(depth_group != "NA")
p <- ggplot(count_depth) +
  geom_bar(aes(x=log10(hours_spent)))
ggsave(filename = "figures/REMOS.png", plot = p, width = 15, height = 10, units = "cm")

```
The REMOS spent a highly variable period of time in each depth group.
![Distribution of the number of hours spent by the REMOS at depth](figures/REMOS.png)
`r knitr::kable(summary(count_depth$hours_spent))`

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# calculations as described by de Carlo et al. (2013)
# we consider that mole fraction in air = ppm
# By convention, a negative flux indicates fluxes directed from the atmosphere to the 
# ocean, and a positive flux indicates fluxes directed from the ocean to the atmosphere.
d_all <- d_all %>%
  dplyr::mutate(
    delta_pco2 = pco2_fb_ctd_temp - co2_air, # uatm
    k600 = 0.266 * ws ^ 2, # cm/h Ho et al. (2006)
    Sc = 2073.1 - (125.62 * temp_insitu_ctd) + (3.6276 * temp_insitu_ctd^2) -
      (0.043219 * temp_insitu_ctd^3),    #dimensionless
    k = (k600 * (Sc / 600) ^ -0.5), #cm/h
    k = k/10, #m/h
    alpha = seacarb::K0(
      S = sal_insitu_ctd,
      T = temp_insitu_ctd,
      P = 0,
      Patm = p_air / 1013.25 # from hPa to atm
    ), #mol/(kg atm)
    alpha = alpha * (seacarb::rho(
      S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0
    ) / 1000), # mol/(l atm)
    alpha = alpha * 1000 , # mol/(m3 atm)
    f_air_sea = k * alpha * delta_pco2, # mol/(m2 h 1e6)
    f_air_sea = k * alpha * delta_pco2 * 1e-6 * 1000 # mmol/(m2 h)
  )

p_f_air_sea <- ggplot(data = d_all) +
  geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Air-sea CO2 flux (all data)", x = "Time", y = "CO2 (mmol/(m2 h))") +
  Mytheme(size_labs = 8)
p_f_air_sea
ggsave(filename = "figures/p_f_air_sea.png", plot = p_f_air_sea, width = 20, units = "cm")

air_sea_day <- d_all %>%
  dplyr::select(datetime, f_air_sea) %>%
  dplyr::group_by(lubridate::yday(datetime)) %>%
  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)) %>% #mmol/(m2 d)
  ungroup() %>%
  dplyr::rename(day = 1)

p_f_air_sea_d <- ggplot(data = air_sea_day) +
  geom_point(aes(x = day, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Air-sea CO2 flux (per day)", x = "Julian day", y = "CO2 (mmol/(m2 d))") +
  Mytheme(size_labs = 8)
#p_f_air_sea_d
ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")

air_sea_month <- d_all %>%
  dplyr::select(monthd, f_air_sea) %>%
  dplyr::group_by(monthd) %>%
  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)) %>% #mmol/(m2 d)
  ungroup() %>%
  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
#air_sea_month
p_f_air_sea_month <- ggplot(data = air_sea_month) +
  geom_point(aes(x = montht, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
  lims(y = c(-3000, 0)) +
  labs(title = "Air-sea CO2 flux (per month)", x = "Month", y = "CO2 (mmol/(m2 month))") +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_month, width = 20, units = "cm")

p <- p_f_air_sea / p_f_air_sea_d / p_f_air_sea_month
ggsave(filename = "figures/air-sea_CO2_flux.png", plot = p, width = 20, units = "cm")
knitr::include_graphics("figures/air-sea_CO2_flux.png")

# For paper
size_point <- 1.5 # size of data points
alpha <- 1 #transparency
size_labs <- 14 # font size labels
# temp_insitu_11m
ts_air_sea <- air_sea_month %>%
  ggplot(aes(x = montht, y = f_air_sea / 1000), na.rm = TRUE) +
  geom_col(colour="blue", fill = "blue",  alpha = alpha) +
  lims(y = c(-3, 0)) +
  geom_hline(yintercept = 0) +
  labs(title=NULL, 
       x="Month", 
       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
  Mytheme(size_labs = size_labs) +
  theme(aspect.ratio=0.5,
        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
        axis.title.x = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14)
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_air_sea
ggsave(filename = "figures/ts_air_sea.png", plot = ts_air_sea, width = 20, units = "cm")
ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea, width = 15, height = 10, units = "cm")
#rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
```

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Same as above but we correct pCO2 by adding 17 uatm as we show above that pCO2 at 11 m
# underestimates pCO2 at 0-4m (hence overestimates CO2 uptake)
# round(summary(tmp$delta_pco2_fb_remos_monthly))[[4]]
d_all <- d_all %>%
  dplyr::mutate(
    delta_pco2_corr = (pco2_fb_ctd_temp + 17) - co2_air,
    k600 = 0.266 * ws ^ 2, # cm/h Ho et al. (2006)
    Sc = 2073.1 - (125.62 * temp_insitu_ctd) + (3.6276 * temp_insitu_ctd^2) -
      (0.043219 * temp_insitu_ctd^3),    #dimensionless
    k = (k600 * (Sc / 600) ^ -0.5), #cm/h
    k = k/10, #m/h
    alpha = seacarb::K0(
      S = sal_insitu_ctd,
      T = temp_insitu_ctd,
      P = 0,
      Patm = p_air / 1013.25 # from hPa to atm
    ), #mol/(kg atm)
    alpha = alpha * (seacarb::rho(
      S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0
    ) / 1000), # mol/(l atm)
    alpha = alpha * 1000 , # mol/(m3 atm)
    f_air_sea_corr = k * alpha * delta_pco2_corr, # mol/(m2 h 1e6)
    f_air_sea_corr = k * alpha * delta_pco2_corr * 1e-6 * 1000 # mmol/(m2 h)
  )
air_sea_corr_month <- d_all %>%
  dplyr::select(monthd, f_air_sea_corr) %>%
  dplyr::group_by(monthd) %>%
  dplyr::summarise(f_air_sea_corr = 24 * mean(f_air_sea_corr, na.rm = TRUE)) %>% #mol/(m2 d)
  ungroup() %>%
  dplyr::mutate(f_air_sea_corr = days_in_month(monthd) * f_air_sea_corr) %>% 
  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
#air_sea_month
p_f_air_sea_corr_month <- ggplot(data = air_sea_corr_month) +
  geom_point(aes(x = montht, y = f_air_sea_corr), col = "blue", size = 2, na.rm = TRUE) +
  #scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  #lims(y = c(-3, 0)) +
  labs(title = "Air-sea CO2 flux (per month) with corrected data", x = "Month", y = "CO2 (mmol/(m2 month))") +
  Mytheme(size_labs = 8)
p_f_air_sea_corr_month
ggsave(filename = "figures/f_air_sea_corr_month.png", plot = p_f_air_sea_corr_month, width = 20, units = "cm")
# # combine without and with correction
# p <- p_f_air_sea_month / p_f_air_sea_corr_month
# ggsave(filename = "figures/air-sea_CO2_flux_comp.png", plot = p, width = 20, units = "cm")
# knitr::include_graphics("figures/air-sea_CO2_flux_comp.png")
#rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
# Figure with and without correction on same plot
```

```{r monthly air-sea for paper, echo=FALSE, message= FALSE, warning=FALSE}
air_sea_month$corr <- rep("no", length=12)
air_sea_corr_month$corr <- rep("yes", length=12)

air_sea <- dplyr::left_join(air_sea_month, air_sea_corr_month, by = "montht") %>% 
  #dplyr::mutate(air_sea_corr_month = air_sea_corr_month/1000) %>% 
  dplyr::select(montht, f_air_sea, f_air_sea_corr) %>% 
  tidyr::pivot_longer(!montht, names_to = "corr", values_to = "air_sea")
ggplot(data = air_sea) +
  geom_point(aes(x = montht, y = air_sea, colour = factor(corr)))
```

The annual air-sea CO2 flux is
`r round(sum(air_sea_month$f_air_sea/1000), digits = 1)` and
`r round(sum(air_sea_corr_month$f_air_sea_corr/1000), digits = 1)` mol CO2/(m2
year) without and with correction, respectively. Or `r round(sum(air_sea_month$f_air_sea*(12/44)/1000), digits = 1)` and
`r round(sum(air_sea_corr_month$f_air_sea_corr*(12/44)/1000), digits = 1)` mol C/(m2
year)

>>>>

count_depth <- depth_time(tmp) %>% 
  dplyr::filter(depth_group != "NA")
p <- ggplot(count_depth) +
  geom_bar(aes(x=log10(hours_spent)))
ggsave(filename = "figures/REMOS.png", plot = p, width = 15, height = 10, units = "cm")
summary(count_depth$hours_spent)
```
The REMOS spent a highly variable period of time in each depth group.
![Distribution of the number of hours spent by the REMOS at depth](figures/REMOS.png)

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# calculations as described by de Carlo et al. (2013)
# we consider that mole fraction in air = ppm
# By convention, a negative flux indicates fluxes directed from the atmosphere to the 
# ocean, and a positive flux indicates fluxes directed from the ocean to the atmosphere.
d_all <- d_all %>%
  dplyr::mutate(
    delta_pco2 = pco2_fb_ctd_temp - co2_air, # uatm
    k600h = 0.266 * ws ^ 2, # cm/h Ho et al. (2006)
    k600d = 0.143 * ws ^ 2, # cm/h Dobashi and Ho (2023)
    Sc = 2073.1 - (125.62 * temp_insitu_ctd) + (3.6276 * temp_insitu_ctd^2) -
      (0.043219 * temp_insitu_ctd^3),    #dimensionless
    kh = (k600h * (Sc / 600) ^ -0.5), #cm/h
    kd = (k600d * (Sc / 600) ^ -0.5), #cm/h
   kh = kh/10, #m/h
   kd = kd/10, #m/h
    alpha = seacarb::K0(
      S = sal_insitu_ctd,
      T = temp_insitu_ctd,
      P = 0,
      Patm = p_air / 1013.25 # from hPa to atm
    ), #mol/(kg atm)
    alpha = alpha * (seacarb::rho(
      S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0) / 1000), # mol/(l atm)
    alpha = alpha * 1000 , # mol/(m3 atm)
    f_air_sea_h = kh * alpha * delta_pco2, # mol/(m2 h 1e6)
    f_air_sea_h = kh * alpha * delta_pco2 * 1e-6 * 1000, # mmol/(m2 h)
    f_air_sea_d = kd * alpha * delta_pco2, # mol/(m2 h 1e6)
    f_air_sea_d = kd * alpha * delta_pco2 * 1e-6 * 1000 # mmol/(m2 h)
  )

p_f_air_sea_h <- ggplot(data = d_all) +
  geom_point(aes(x = datetime, y = f_air_sea_h), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Air-sea CO2 flux (all data) with Ho's formulation", x = "Time", y = "CO2 (mmol/(m2 h))") +
  Mytheme(size_labs = 8)
p_f_air_sea_h
ggsave(filename = "figures/p_f_air_sea_h.png", plot = p_f_air_sea_h, width = 20, units = "cm")

air_sea_day_h <- d_all %>%
  dplyr::select(datetime, f_air_sea_h) %>%
  dplyr::group_by(lubridate::yday(datetime)) %>%
  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_h, na.rm = TRUE)) %>% #mmol/(m2 d)
  ungroup() %>%
  dplyr::rename(day = 1)

p_f_air_sea_day_h <- ggplot(data = air_sea_day_h) +
  geom_point(aes(x = day, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Air-sea CO2 flux (per day) with Ho's formulation", x = "Julian day", y = "CO2 (mmol/(m2 d))") +
  Mytheme(size_labs = 8)
#p_f_air_sea_d
ggsave(filename = "figures/f_air_sea_day_h.png", plot = p_f_air_sea_day_h, width = 20, units = "cm")

air_sea_month_h <- d_all %>%
  dplyr::select(monthd, f_air_sea_h) %>%
  dplyr::group_by(monthd) %>%
  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_h, na.rm = TRUE)) %>% #mmol/(m2 d)
  ungroup() %>%
  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
#air_sea_month
p_f_air_sea_month_h <- ggplot(data = air_sea_month_h) +
  geom_point(aes(x = montht, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
  lims(y = c(-3000, 0)) +
  labs(title = "Air-sea CO2 flux (per month) with Ho's formulation", x = "Month", y = "CO2 (mmol/(m2 month))") +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/f_air_sea_m_h.png", plot = p_f_air_sea_month_h, width = 20, units = "cm")

p <- p_f_air_sea_h / p_f_air_sea_day_h / p_f_air_sea_month_h
ggsave(filename = "figures/air-sea_CO2_flux_h.png", plot = p, width = 20, units = "cm")
knitr::include_graphics("figures/air-sea_CO2_flux_h.png")

# For paper Ho only
size_point <- 1.5 # size of data points
alpha <- 1 #transparency
size_labs <- 14 # font size labels
# temp_insitu_11m
tmp <- d_all %>% 
  dplyr::select(montht, f_air_sea_h)
ts_air_sea_h <- tmp %>%
  ggplot(aes(x = montht, y = f_air_sea_h / 1000), na.rm = TRUE) +
  geom_col(colour="blue", fill = "blue",  alpha = alpha) +
  lims(y = c(-5, 0)) +
  geom_hline(yintercept = 0) +
  labs(title=NULL, 
       x="Month", 
       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
  Mytheme(size_labs = size_labs) +
  theme(aspect.ratio=0.5,
        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
        axis.title.x = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14)
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_air_sea_h
ggsave(filename = "figures/ts_air_sea_h.png", plot = ts_air_sea_h, width = 20, units = "cm")
ggsave(filename = "figures/essd/ts_air_sea_h.pdf", plot = ts_air_sea_h, width = 15, height = 10, units = "cm")

# For paper Dobashi & Ho 
# Above, only Ho's formulation is dealt with
# make tibble for Dobashi's formulation to be used in plot
air_sea_month_d <- d_all %>%
  dplyr::select(monthd, f_air_sea_d) %>%
  dplyr::group_by(monthd) %>%
  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_d, na.rm = TRUE)) %>% #mmol/(m2 d)
  ungroup() %>%
  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
# air_sea_month_d <- d_all %>%
#   dplyr::select(monthd, f_air_sea_d) %>%
#   dplyr::group_by(monthd) %>%
#   dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_d, na.rm = TRUE)) %>% #mmol/(m2 d)
#   ungroup() %>%
#   dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
#   dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))

# Now we combine Ho's and Dobashi's formulations
air_sea_month_h <- air_sea_month_h %>% 
  dplyr::rename(f_air_sea_h = f_air_sea) %>% 
  dplyr::select(-monthd)
air_sea_month_d <- air_sea_month_d %>% 
  dplyr::rename(f_air_sea_d = f_air_sea) %>% 
  dplyr::select(-monthd)
air_sea <- dplyr::left_join(air_sea_month_h, air_sea_month_d) 
air_sea_long <- air_sea %>% 
  pivot_longer(!montht, names_to = "Formulation", values_to = "f_air_sea")

size_point <- 1.5 # size of data points
alpha <- 1 #transparency
size_labs <- 14 # font size labels
# temp_insitu_11m
ts_air_sea <- air_sea_long %>%
  ggplot(aes(x = montht, y = f_air_sea / 1000, fill = Formulation), na.rm = TRUE) +
  geom_col(alpha = alpha, position = "dodge") +
  lims(y = c(-3, 0)) +
  geom_hline(yintercept = 0) +
  labs(title=NULL, 
       x="Month", 
       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
  scale_fill_discrete(name = "", labels = c("Dobashi & Ho (2023)", "Ho et al. (2006)")) +
  Mytheme(size_labs = size_labs) +
  theme(aspect.ratio=0.5,
        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
        axis.title.x = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14)
        ) 
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_air_sea
ggsave(filename = "figures/ts_air_sea.png", plot = ts_air_sea, width = 20, units = "cm")
ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea, width = 15, height = 10, units = "cm")
```

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Same as above but we correct pCO2 by adding 17 uatm as we show above that pCO2 at 11 m
# underestimates pCO2 at 0-4m (hence overestimates CO2 uptake)
# round(summary(tmp$delta_pco2_fb_remos_monthly))[[4]]
d_all <- d_all %>%
  dplyr::mutate(
    delta_pco2_corr = (pco2_fb_ctd_temp + 17) - co2_air, # uatm
    k600h = 0.266 * ws ^ 2, # cm/h Ho et al. (2006)
    k600d = 0.143 * ws ^ 2, # cm/h Dobashi and Ho (2023)
    Sc = 2073.1 - (125.62 * temp_insitu_ctd) + (3.6276 * temp_insitu_ctd^2) -
      (0.043219 * temp_insitu_ctd^3),    #dimensionless
    kh = (k600h * (Sc / 600) ^ -0.5), #cm/h
    kd = (k600d * (Sc / 600) ^ -0.5), #cm/h
   kh = kh/10, #m/h
   kd = kd/10, #m/h
    alpha = seacarb::K0(
      S = sal_insitu_ctd,
      T = temp_insitu_ctd,
      P = 0,
      Patm = p_air / 1013.25 # from hPa to atm
    ), #mol/(kg atm)
    alpha = alpha * (seacarb::rho(
      S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0) / 1000), # mol/(l atm)
    alpha = alpha * 1000 , # mol/(m3 atm)
    f_air_sea_h_corr = kh * alpha * delta_pco2_corr, # mol/(m2 h 1e6)
    f_air_sea_h_corr = kh * alpha * delta_pco2_corr * 1e-6 * 1000, # mmol/(m2 h)
    f_air_sea_d_corr = kd * alpha * delta_pco2_corr, # mol/(m2 h 1e6)
    f_air_sea_d_corr = kd * alpha * delta_pco2_corr * 1e-6 * 1000 # mmol/(m2 h)
  )

air_sea_month_h_corr <- d_all %>%
  dplyr::select(monthd, f_air_sea_h_corr) %>%
  dplyr::group_by(monthd) %>%
  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_h_corr, na.rm = TRUE)) %>% #mmol/(m2 d)
  ungroup() %>%
  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))

# For paper Dobashi & Ho 
# Above, only Ho's formulation is dealt with
# make tibble for Dobashi's formulation to be used in plot
air_sea_month_d_corr <- d_all %>%
  dplyr::select(monthd, f_air_sea_d_corr) %>%
  dplyr::group_by(monthd) %>%
  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_d_corr, na.rm = TRUE)) %>% #mmol/(m2 d)
  ungroup() %>%
  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))

# air_sea_month_d <- d_all %>%
#   dplyr::select(monthd, f_air_sea_d) %>%
#   dplyr::group_by(monthd) %>%
#   dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_d, na.rm = TRUE)) %>% #mmol/(m2 d)
#   ungroup() %>%
#   dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
#   dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))

# Now we combine Ho's and Dobashi's formulations
air_sea_month_h_corr <- air_sea_month_h_corr %>% 
  dplyr::rename(f_air_sea_h_corr = f_air_sea) %>% 
  dplyr::select(-monthd)
air_sea_month_d_corr <- air_sea_month_d_corr %>% 
  dplyr::rename(f_air_sea_d_corr = f_air_sea) %>% 
  dplyr::select(-monthd)
air_sea <- dplyr::left_join(air_sea_month_h_corr, air_sea_month_d_corr) 
air_sea_long <- air_sea %>% 
  pivot_longer(!montht, names_to = "Formulation", values_to = "f_air_sea")

size_point <- 1.5 # size of data points
alpha <- 1 #transparency
size_labs <- 14 # font size labels
# temp_insitu_11m
ts_air_sea_corr <- air_sea_long %>%
  ggplot(aes(x = montht, y = f_air_sea / 1000, fill = Formulation), na.rm = TRUE) +
  geom_col(alpha = alpha, position = "dodge") +
  lims(y = c(-3, 0)) +
  geom_hline(yintercept = 0, size = 0.5) +
  labs(title=NULL, 
       x="Month", 
       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
  scale_fill_discrete(name = "", labels = c("Dobashi & Ho (2023)", "Ho et al. (2006)")) +
  Mytheme(size_labs = size_labs) +
  theme(aspect.ratio=0.5,
        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
        axis.title.x = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14)
        ) 
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_air_sea_corr
ggsave(filename = "figures/ts_air_sea_corr.png", plot = ts_air_sea_corr, width = 20, units = "cm")
ggsave(filename = "figures/essd/ts_air_sea_corr.pdf", plot = ts_air_sea_corr, width = 15, height = 10, units = "cm")

# d_all <- d_all %>%
#   dplyr::mutate(
#     delta_pco2_corr = (pco2_fb_ctd_temp + 17) - co2_air,
#     k600 = 0.266 * ws ^ 2, # cm/h Ho et al. (2006)
#     Sc = 2073.1 - (125.62 * temp_insitu_ctd) + (3.6276 * temp_insitu_ctd^2) -
#       (0.043219 * temp_insitu_ctd^3),    #dimensionless
#     k = (k600 * (Sc / 600) ^ -0.5), #cm/h
#     k = k/10, #m/h
#     alpha = seacarb::K0(
#       S = sal_insitu_ctd,
#       T = temp_insitu_ctd,
#       P = 0,
#       Patm = p_air / 1013.25 # from hPa to atm
#     ), #mol/(kg atm)
#     alpha = alpha * (seacarb::rho(
#       S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0
#     ) / 1000), # mol/(l atm)
#     alpha = alpha * 1000 , # mol/(m3 atm)
#     f_air_sea_corr = k * alpha * delta_pco2_corr, # mol/(m2 h 1e6)
#     f_air_sea_corr = k * alpha * delta_pco2_corr * 1e-6 * 1000 # mmol/(m2 h)
#   )
# air_sea_corr_month <- d_all %>%
#   dplyr::select(monthd, f_air_sea_corr) %>%
#   dplyr::group_by(monthd) %>%
#   dplyr::summarise(f_air_sea_corr = 24 * mean(f_air_sea_corr, na.rm = TRUE)) %>% #mol/(m2 d)
#   ungroup() %>%
#   dplyr::mutate(f_air_sea_corr = days_in_month(monthd) * f_air_sea_corr) %>% 
#   dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
# #air_sea_month
# p_f_air_sea_corr_month <- ggplot(data = air_sea_corr_month) +
#   geom_point(aes(x = montht, y = f_air_sea_corr), col = "blue", size = 2, na.rm = TRUE) +
#   #scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
#   #lims(y = c(-3, 0)) +
#   labs(title = "Air-sea CO2 flux (per month) with corrected data", x = "Month", y = "CO2 (mmol/(m2 month))") +
#   Mytheme(size_labs = 8)
# p_f_air_sea_corr_month
# ggsave(filename = "figures/f_air_sea_corr_month.png", plot = p_f_air_sea_corr_month, width = 20, units = "cm")
# # # combine without and with correction
# # p <- p_f_air_sea_month / p_f_air_sea_corr_month
# # ggsave(filename = "figures/air-sea_CO2_flux_comp.png", plot = p, width = 20, units = "cm")
# # knitr::include_graphics("figures/air-sea_CO2_flux_comp.png")
# #rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
# # Figure with and without correction on same plot
```

```{r monthly air-sea for paper, echo=FALSE, message= FALSE, warning=FALSE}
# air_sea_month$corr <- rep("no", length=12)
# air_sea_corr_month$corr <- rep("yes", length=12)
# 
# air_sea <- dplyr::left_join(air_sea_month, air_sea_corr_month, by = "montht") %>% 
#   #dplyr::mutate(air_sea_corr_month = air_sea_corr_month/1000) %>% 
#   dplyr::select(montht, f_air_sea, f_air_sea_corr) %>% 
#   tidyr::pivot_longer(!montht, names_to = "corr", values_to = "air_sea")
# ggplot(data = air_sea) +
#   geom_point(aes(x = montht, y = air_sea, colour = factor(corr)))
```

The annual air-sea CO2 flux with the Ho et al. (2006) formulation is
`r round(sum(air_sea_month_h$f_air_sea_h/1000), digits = 1)` and
`r round(sum(air_sea_month_h_corr$f_air_sea_h_corr/1000), digits = 1)` mol CO2/(m2
year) without and with correction, respectively. Or `r round(sum(air_sea_month_h$f_air_sea_h*(12/44)/1000), digits = 1)` and
`r round(sum(air_sea_month_h_corr$f_air_sea_h_corr*(12/44)/1000), digits = 1)` mol C/(m2
year)

The annual air-sea CO2 flux with the Dobashi et al. (2023) formulation is
`r round(sum(air_sea_month_d$f_air_sea_d/1000), digits = 1)` and
`r round(sum(air_sea_month_d_corr$f_air_sea_d_corr/1000), digits = 1)` mol CO2/(m2
year) without and with correction, respectively. Or `r round(sum(air_sea_month_d$f_air_sea_d*(12/44)/1000), digits = 1)` and
`r round(sum(air_sea_month_d_corr$f_air_sea_d_corr*(12/44)/1000), digits = 1)` mol C/(m2
year)
